PANCHANGE_analysis

### 2020-09-02 PANCHANGE_analysis.Rmd
Added chunks to create 3 datasets for the analyses, excluding individuals on varying criteria.

++MD: I had to cancel this chunk while running because it took too long - there are 473 variables in this dataset, so I don't think summarising all at once is useful!
```{r dat.coping summary, eval=FALSE, include=FALSE}
summarytools::dfSummary(
  dat.raw,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

@@

```{r Collapse Ethnicity}
dat.raw <- dat.raw %>%
  mutate(Ethnicity_collapsed_numeric =
           case_when(
             Ethnicity_numeric == 1 ~ 0,
             Ethnicity_numeric == 2 ~ 1,
             Ethnicity_numeric == 3 ~ 2,
             Ethnicity_numeric == 4 ~ 3,
             Ethnicity_numeric == 5 ~ 3,
             Ethnicity_numeric == 6 ~ 4
           )
  )

@@

# Exclusion

## COPING
Filter data frame to exclude participants that never answered COPING
```{r exclusion criteria dat}
dat.2.timepoints <- dat.raw %>%
  filter(
    (data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")
  )

dim(dat.2.timepoints)
```

@@

```{r}
dat.2.timepoints %>%
  select(age_category) %>%
  filter(is.na(age_category))
```

Exclusion
```{r Exclusion}
dat <- dat.2.timepoints %>%

```{r dimensions of total dat}
dim(dat)
```

```{r}
dat %>%
  freq(disorders_total_count)
```

>>>>

++MD: I had to cancel this chunk while running because it took too long - there are 473 variables in this dataset, so I don't think summarising all at once is useful!
```{r dat.coping summary, eval=FALSE, include=FALSE}
#summarytools::dfSummary(
#  dat.raw,
#  graph.col = F,
#  valid.col = F,
#  labels.col = F)
```

@@

++MD: Need to decide what to do with the Arab grouping.
```{r Collapse Ethnicity}
dat.raw <- dat.raw %>%
  mutate(Ethnicity_collapsed_numeric =
           case_when(
             Ethnicity_numeric == 1 ~ 0,
             Ethnicity_numeric == 2 ~ 1,
             Ethnicity_numeric == 3 ~ 2,
             Ethnicity_numeric == 4 ~ 3,
             Ethnicity_numeric == 5 ~ 3,
             Ethnicity_numeric == 6 ~ 4
           )
  )

@@

# Exclusion
Filter data frame to create 3 datasets:
  1. Diagnoses analyses
        i. Exclude individuals with NA for MHD
  2. Retrospective - baseline change anlyses
        i. Exclude individuals with NAs for:
              1. MHD
              2. Age
              3. Gender
  3. Prepandemic - baseline change analyses
          i. Exclude individuals with NAs for:
              1. MHD
              2. Age
              3. Gender
          ii. Exclude individuals with prepandemic data collected after 1st March.

Diagnoses analyses
Exclude individuals with NA for the MHD categories
```{r exclusion criteria for diagnoses analysis}
dat.mhd <- dat.raw %>%
  filter(
    !is.na(depressive_disorders) &
      !is.na(eating_disorders) &
      !is.na(psychotic_disorders) &
      !is.na(obsessive_compulsive_disorders) &
      !is.na(autism_spectrum_disorder) &
      !is.na(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) &
      !is.na(mhd.posttraumatic_stress_disorder_ptsd_numeric)
  )

dim(dat.mhd)

@@

Retro-baseline analyses
Exclude individuals with NA for MHD, age, gender
```{r exclusion criteria for retro-baseline analysis}
dat.retro <- dat.mhd %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      !is.na(age_category) &
      !is.na(Gender_collapsed)
  )

dim(dat.retro)
```

Prepan-baseline analyses
Exclude individuals with NA for MHD, age, gender; exclude if prepan data collected after 1 March
```{r exclusion criteria for prepan-baseline analysis}
dat.prepan <- dat.mhd %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      !is.na(age_category) &
      !is.na(Gender_collapsed) &
      prepandemic_march_1_numeric == 1
  )

dim(dat.prepan)
```

```{r dimensions of total dat}
dim(dat.raw)
```

```{r disorders total count}
dat.raw %>%
  freq(disorders_total_count)
```
